\cleardoublepage
\chapternonum{附录~作者简历及攻读博士学位期间发表的学术论文}

\noindent \textbf{作者简历}

\noindent2012.09-2016.06~~~~电子科技大学~~~~生物医学工程专业~~~~工学学士

\noindent2018.10-2021.05~~~~北卡罗来纳大学教堂山分校~~~~联合培养博士

\noindent2016.09-2021.06~~~~浙江大学~~~~生物医学工程专业~~~~工学博士

\bigskip

\noindent \textbf{攻读博士学位期间发表的学术论文}

\ifthenelse{\equal{\BlindReview}{true}}%
        {
        \noindent [1] Anonymized paper title[J]. IEEE transactions on medical imaging, 2021, 已发表。（SCI，\textbf{一作}，IF：6.685）
        
        \noindent [2] Anonymized paper title[J]. IEEE transactions on medical imaging, 2021, 已录用。（SCI，\textbf{一作}，IF：6.685）
        
        \noindent [3] Anonymized paper title[C]. International Conference on Medical Image Computing and Computer Assisted Intervention, 2019, 已发表。（EI，\textbf{一作}，医学图像分析领域顶级会议）
        
        \noindent [4] Anonymized paper title[C]. International Conference on Information Processing in Medical Imaging, 2019, 已发表。（EI，\textbf{一作}，医学图像分析领域顶级会议）
        
        \noindent [5] Anonymized paper title[C]. 2019 IEEE 16th International Symposium on Biomedical Imaging, 2019, 已发表。（EI，\textbf{一作}，医学图像分析领域顶级会议）
        
        \noindent [6] Anonymized paper title[C]. International Workshop on Machine Learning in Medical Imaging, 2020, 已发表。（EI，\textbf{一作}）
        
        \noindent [7] Anonymized paper title[J]. Neuroimage, 2021, 已发表。（SCI，二作，IF：5.902） 
        
        \noindent [8] Anonymized paper title[C]. International Conference on Medical Image Computing and Computer Assisted Intervention, 2019, 已发表。（EI，二作，医学图像分析领域顶级会议）
        
        \noindent [9] Anonymized paper title[J]. Nature communications, 2020, 已发表。（SCI，三作，IF：12.121）
        
        \noindent [10] Anonymized paper title[C]. International Conference on Medical Image Computing and Computer Assisted Intervention, 2020, 已发表。（EI，三作，医学图像分析领域顶级会议）
        
        \noindent [11] Anonymized paper title[C]. International Conference on Medical Image Computing and Computer Assisted Intervention, 2020, 已发表。（EI，三作，医学图像分析领域顶级会议）
        
        \noindent [12] Anonymized paper title[C]. International Workshop on Machine Learning in Medical Imaging, 2020, 已发表。（EI，三作）
        
        \noindent [13] Anonymized paper title[C]. 2020 IEEE 17th International Symposium on Biomedical Imaging, 2020, 已发表。（EI，三作，医学图像分析领域顶级会议）
        
        \noindent [14] Anonymized paper title[J]. 航天医学与医学工程, 2018, 已发表。（二作，中文核心期刊）
        
        \noindent [15] Anonymized paper title[J]. 航天医学与医学工程, 2020, 已发表。（二作，中文核心期刊）
        }
        
        
        
        {
        \noindent [1] \textbf{Fenqiang Zhao}, Zhengwang Wu, Li Wang, Weili Lin, John H Gilmore, Shunren Xia, Dinggang Shen, Gang Li. Spherical Deformable U-Net: Application to Cortical Surface Parcellation and Development Prediction[J], IEEE transactions on medical imaging, 2021, 40(4): 1217-1228.（SCI，IF：6.685）
        
        \noindent [2] \textbf{Fenqiang Zhao}, Zhengwang Wu, Fan Wang, Weili Lin, Shunren Xia, Dinggang Shen, Li Wang, Gang Li. S3Reg: Superfast Spherical Surface Registration Based on Deep Learning[J], IEEE transactions on medical imaging, 2021.（SCI，IF：6.685，已录用）
        
        \noindent [3] \textbf{Fenqiang Zhao}, Zhengwang Wu, Li Wang, Weili Lin, Shunren Xia, Gang Li. A Deep Network for Joint Registration and Parcellation of Cortical Surfaces[C], International Conference on Medical Image Computing and Computer Assisted Intervention, 2021.（EI，医学图像分析领域顶级会议，已录用）
        
        \noindent [4] \textbf{Fenqiang Zhao}, Zhengwang Wu, Li Wang, Weili Lin, Shunren Xia, Gang Li. Learning 4D Infant Cortical Surface Atlas with Unsupervised Spherical Networks[C], International Conference on Medical Image Computing and Computer Assisted Intervention, 2021.（EI，医学图像分析领域顶级会议，已录用）
        
        \noindent [5] \textbf{Fenqiang Zhao}, Shunren Xia, Zhengwang Wu, Dingna Duan, Li Wang, Weili Lin, John Gilmore, Dinggang Shen, Gang Li. Spherical U-Net on Cortical Surfaces: Methods and Applications[C], International Conference on Information Processing in Medical Imaging, 2019: 855-866.（EI，医学图像分析领域顶级会议）
        
        \noindent [6] \textbf{Fenqiang Zhao}, Zhengwang Wu, Li Wang, Weili Lin, Shunren Xia, Dinggang Shen, Gang Li. Harmonization of Infant Cortical Thickness Using Surface-to-Surface Cycle-Consistent Adversarial Networks[C], International Conference on Medical Image Computing and Computer Assisted Intervention, 2019: 475-483.（EI，医学图像分析领域顶级会议，口头报告）
        
        \noindent [7] \textbf{Fenqiang Zhao}, Shunren Xia, Zhengwang Wu, Zengsi Chen, Li Wang, Weili Lin, John Gilmore, Dinggang Shen, Gang Li. Spherical U-Net for Infant Cortical Surface Parcellation[C], IEEE 16th International Symposium on Biomedical Imaging, 2019: 1882-1886.（EI，医学图像分析领域顶级会议，口头报告）
        
        \noindent [8] \textbf{Fenqiang Zhao}, Zhengwang Wu, Li Wang, Weili Lin, Shunren Xia, Dinggang Shen, Gang Li. Unsupervised Learning for Spherical Surface Registration[C], International Workshop on Machine Learning in Medical Imaging, 2020: 373-383.（EI）
        
        \noindent [9] Tao Zhong, \textbf{Fenqiang Zhao}, Yuchen Pei, Zhenyuan Ning, Lufan Liao, Zhengwang Wu, Yuyu Niu, Li Wang, Dinggang Shen, Yu Zhang, Gang Li. DIKA-Nets: Domain-invariant Knowledge-guided Attention Networks for Brain Skull Stripping of Early Developing Macaques[J], Neuroimage, 2021, 227: 117649.（SCI，IF：5.902） 
        
        \noindent [10] Zhengwang Wu, \textbf{Fenqiang Zhao}, Jing Xia, Li Wang, Gang Li, Dinggang Shen. Intrinsic Patch-Based Cortical Anatomical Parcellation using Graph Convolutional Neural Network on Surface Manifold[C], International Conference on Medical Image Computing and Computer Assisted Intervention, 2019: 492-500.（EI，医学图像分析领域顶级会议）
        
        \noindent [11] Luhong Jin, Bei Liu, \textbf{Fenqiang Zhao}, Stephen Hahn, Bowei Dong, Ruiyan Song, Timothy C. Elston, Yingke Xu, Klaus M. Hahn. Deep Learning Enables Structured Illumination Microscopy with Low Light Levels and Enhanced Speed[J], Nature communications, 2020, 11(1): 1-7.（SCI，IF：12.121）
        
        \noindent [12] Lufan Liao, Xin Zhang, \textbf{Fenqiang Zhao}, Tao Zhong, Yuchen Pei, Xiangmin Xu, Li Wang, He Zhang, Dinggang Shen, Gang Li. Joint Image Quality Assessment and Brain Extraction of Fetal MRI Using Deep Learning[C], International Conference on Medical Image Computing and Computer Assisted Intervention, 2020: 415-424.（EI，医学图像分析领域顶级会议）
        
        \noindent [13] Tao Zhong, Yu Zhang, \textbf{Fenqiang Zhao}, Yuchen Pei, Lufan Liao, Zhenyuan Ning, Li Wang, Dinggang Shen, Gang Li. Domain-Invariant Prior Knowledge Guided Attention Networks for Robust Skull Stripping of Developing Macaque Brains[C],  International Conference on Medical Image Computing and Computer Assisted Intervention, 2020: 22-32.（EI，医学图像分析领域顶级会议）
        
        \noindent [14] Yuchen Pei, Lisheng Wang, \textbf{Fenqiang Zhao}, Tao Zhong, Lufan Liao, Dinggang Shen, Gang Li. Anatomy-Guided Convolutional Neural Network for Motion Correction in Fetal Brain MRI[C], International Workshop on Machine Learning in Medical Imaging, 2020: 384-393.（EI）
        
        \noindent [15] Lufan Liao, Xin Zhang, \textbf{Fenqiang Zhao}, Jingjiao Lou, Li Wang, Xiangmin Xu, He Zhang, Gang Li. Multi-branch Deformable Convolutional Neural Network with Label Distribution Learning for Fetal Brain Age Prediction[C], IEEE 17th International Symposium on Biomedical Imaging, 2020.（EI，医学图像分析领域顶级会议）
        
        \noindent [16] 邱陈辉，\textbf{赵奋强}，王媛媛，夏顺仁。基于非下采样剪切波变换的PET/SPECT和MR图像融合[J]。航天医学与医学工程，2018, 31(3): 353-358。（浙大一级期刊）

        \noindent [17] 邱陈辉，\textbf{赵奋强}，段丁娜，夏顺仁。基于卷积稀疏表示的鲁棒性PET和CT图像融合方法[J]。航天医学与医学工程，2020, 33(1): 66-73。（浙大一级期刊）
        }